\documentclass[cfonts]{nostarch}
\usepackage{natbib}
\usepackage{nshyper}

% There has to be a better way do to this, but after wasting a full
% day, I wasn't able to find it (using the fontspec package kills the
% nostarch style)
\usepackage{newunicodechar}
\newunicodechar{→}{$\triangleright$}
\newunicodechar{←}{$\leftarrow$}
\newunicodechar{“}{``}
\newunicodechar{”}{''}
\newunicodechar{’}{'}
\newunicodechar{π}{$\pi$}
\newunicodechar{½}{$\frac{1}{2}$}
\newunicodechar{⅓}{$\frac{1}{3}$}
\newunicodechar{¼}{$\frac{1}{4}$}
\newunicodechar{…}{...}
\newunicodechar{×}{$\times$}
\newunicodechar{β}{\ss}
\newunicodechar{ϕ}{$\varphi$}
\newunicodechar{≈}{$\approx$}
\newunicodechar{—}{---}

% epigraph is used to style chapter quotes
\usepackage{epigraph}
\setlength{\epigraphwidth}{.8\textwidth}
\setlength{\epigraphrule}{0pt}

\graphicspath{ {../} }
\makeindex

\begin{document}

\frontmatter

\author{Marijn Haverbeke}

\title{Eloquent JavaScript}

\subtitle{A Modern Introduction to Programming}

\makehalftitle

\maketitle

\begin{copyrightpage}
  \textbf{\sffamily\MakeUppercase{Pellentesque habitant morbi.}}
  Copyright \textcopyright{} 2014 by Marijn Haverbeke

  This work is licensed under a Creative Commons
  attribution-noncommercial license
  (\url{http://creativecommons.org/licenses/by-nc/3.0/}).

For information on book distributors or translations, please contact
No Starch Press, Inc. directly: \\
No Starch Press, Inc.\\
555 De Haro Street, Suite 250, San Francisco, CA 94107\\
phone: 415.863.9900; fax: 415.863.9950; info@nostarch.com; www.nostarch.com\\

No Starch Press and the No Starch Press logo are registered trademarks
of No Starch Press, Inc. Other product and company names mentioned
herein may be the trademarks of their respective owners. Rather than
use a trademark symbol with every occurrence of a trademarked name, we
are using the names only in an editorial fashion and to the benefit of
the trademark owner, with no intention of infringement of the
trademark.

The information in this book is distributed on an ``As Is'' basis,
without warranty. While every precaution has been taken in the
preparation of this work, neither the author nor No Starch Press, Inc.
shall have any liability to any person or entity with respect to any
loss or damage caused or alleged to be caused directly or indirectly
by the information contained in it.

\end{copyrightpage}

\begin{dedicationpage}
For Lotte and Jan
\end{dedicationpage}

\brieftableofcontents

\tableofcontents

\mainmatter

\input{00_intro.tex}

\input{01_values.tex}

\input{02_program_structure.tex}

\input{03_functions.tex}

\input{04_data.tex}

\input{05_higher_order.tex}

\input{06_object.tex}

\input{07_elife.tex}

\input{08_error.tex}

\input{09_regexp.tex}

\input{10_modules.tex}

\input{11_language.tex}

\input{12_browser.tex}

\input{13_dom.tex}

\input{14_event.tex}

\input{15_game.tex}

\input{16_canvas.tex}

\input{17_http.tex}

\input{18_forms.tex}

\input{19_paint.tex}

\input{20_node.tex}

\input{21_skillsharing.tex}

\input{hints.tex}

\backmatter

\printindex

\updatespage

Visit \url{http://eloquentjavascript.net} for solutions to the
exercises, updates, errata, and other information.

\end{document}
